---
title: "First draft"
author: "Durjoy Sarker"
format:
  html: default
  pdf: default
editor: visual
---

## Introduction

Soil salinity affects germination and seedling growth

```{r}
salinity <- c(0,50,100,150)
germination <- c(95,82,60,40)
plot(salinity, germination, type="b", col = "darkgreen",
     main="The Plot",
     xlab="NaCl concentration (mM)",
     ylab="Germination (%)")
```

### Figure Example: Salinity and Germination

#| label: fig-salinity
#| fig-cap: "Effect of salinity on yard long bean germination"
#| echo: false
#| message: false
#| warning: false
```{r}
library(ggplot2)
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point()
```

As shown in Figure @fig-salinity, germination decreases as salinity  increases
(see Figure @fig-salinity)




### Figure Example: Salinity and Germination

#| label: fig-salinity
#| fig-cap: "Effect of salinity on yard long bean germination"
#| echo: false
#| message: false
#| warning: false
```{r}
library(ggplot2)

# Example plot
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point()
```

As shown in Figure @fig-salinity, germination decreases as salinity increases.  
(see Figure @fig-salinity)
